Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-04-18 rebuttal.md

**issue 6:** This issue is addressed in threats to validity...
> Moreover, slicing needs more time for analysis and running time might become an issue.

**ANSWER:**

### Review 252039:

**ANSWER:**

We kindly thank the reviewer for the feedback on our work. We will make sure that the paper's formality will be improved. Minor issues will also be addressed. We will definitely explore the statistical machine learning approach in future work.

@@

### Review 263473:

**issue 7:** 
Should we try to address this review?
> The work is important and the authors have been very careful with applying a methodological approach. However, it seems that such refactoring contributions seem to better fit into the journal setting where the reviewers can actually take a look at the proposed implementation and the authors are not so constrained with space.

> * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms. That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai? It feels that calling the observation a theorem is a bit  ambitious. Perhaps such property is something to characterize the ranking algorithms by?
> * A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm. It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
> * Perhaps the approach should be called DS-SBFL instead of Tandem-FL?  The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
> * Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
> * Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.

**ANSWER:**

@@

## Review 263474:

**issue 8:** 
> I have not the highest confidence with the field but my feeling is that the problem is interesting and the results are valuable. My only concern is whether the **investigated issue fits the main topics of the conference** (no comment of author(s) helps in this sense). For sure this kind of paper would be more appropriate in conferences on software engineering, validation and testing. In those venues I had proposed acceptance. In this context I’m a little bit puzzled.

**ANSWER:**

We kindly thank the reviewer for the comments on our work. As we mention in section 2, applications of model-based diagnosis to localize software faults have demonstrated that can be framed as dynamic slicing which is the technique proposed to improve software fault localization. Model-based diagnosis is a well-known approach that has been proposed by the diagnosis community. This community develops algorithms and techniques that leverage AI to determine the rootcause of observed faults. We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that IJCAI can be the home to this paper since we are applying AI to improve SBFL.

### 2019-04-18 rebuttal.md

## Review 263474:

**issue 8:** 
> I have not the highest confidence with the field but my feeling is that the problem is interesting and the results are valuable. My only concern is whether the **investigated issue fits the main topics of the conference** (no comment of author(s) helps in this sense). For sure this kind of paper would be more appropriate in conferences on software engineering, validation and testing. In those venues I had proposed acceptance. In this context I’m a little bit puzzled.

**ANSWER:**

We kindly thank the reviewer for the comments on our work. As we mention in section 2, applications of model-based diagnosis to localize software faults have demonstrated that can be framed as dynamic slicing which is the technique proposed to improve software fault localization. Model-based diagnosis is a well-known approach that has been proposed by the diagnosis community. This community develops algorithms and techniques that leverage AI to determine the rootcause of observed faults. We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.

## Other points

### 2019-04-18 rebuttal.md

**issue 6:** This issue is addressed in threats to validity...
> Moreover, slicing needs more time for analysis and running time might become an issue.

**Rebuttal:**

### Review 252039:

**Rebuttal:**

We kindly thank the reviewer for its insights and comments on our work.

We will make sure that the paper's formality will be improved and that minor issues will also be addressed. We will definitely explore the statistical machine learning approach in future work.

@@

### Review 263473:

**Issues:** 
> * An obvious improvement would be to parameterize the approach to  allow plugging in multiple different ranking algorithms. That  immediately raises the question: does the observation that the rank of faulty statements cannot decrease if the slice includes the  faulty statements also work with other ranking algorithms than  Ochiai? It feels that calling the observation a theorem is a bit  ambitious. Perhaps such property is something to characterize the ranking algorithms by?
> * A more labour intensive approach would be to also parameterize  the approach over different slicing implementations, or at least  foresee the need and make it very clear how to change the slicing algorithm. It is very nice that the authors have started with critical slicing as one of the earlier appropriate approaches.
> * Perhaps the approach should be called DS-SBFL instead of Tandem-FL?  The reason being that there are multiple things that could be used  in tandem in the fault localisation context (for example a tandem of  some symbolic FL approach with an additional technique).
> * Theorem 1 is not a theorem, it is rather an observation, because it  depends on the simplifications used by the slicing  algorithm.
> * Theorem 2 is actually a property of the Ochiai ranking formula, not a theorem.

**Rebuttal:**

We thank the reviewer for the feedback provided on our work.

Regarding the question about if claim 2 is also true for other ranking algorithms, there is a possibility this might not be true. To answer your question, the present work needs to be extended. We plan to investigate the veracity of claim 2 using other ranking algorithms, such as, Tarantula, Op2, Barinel and etc. This, however remains for future work.

< Still have to justify why have we not compared with other slicing approaches >

< Not sure what to say about the name, do we agree?>

We agree that our theorems are rather observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed on the paper.

### 2019-04-18 rebuttal.md

**issue 5:** 
> In addition, there is no discussion of drawbacks behind the approach. Spectrum-based fault localization is successful because it does not require a lot of tools and can be more or less easily adapted for other programming languages. This is not the case for slicing. For slicing we require to know not only that a test case is failing but also to identify all output variables that deliver wrong values. In case of exceptions (as discussed a little bit in the paper) we may also use different slicing approaches to improve the results. There is some work on dynamic slicing in case of exceptions.

**issue 6:** This issue is addressed in threats to validity...
> Moreover, slicing needs more time for analysis and running time might become an issue.

**Rebuttal:**

We kindly thank the reviewer for the comments and questions raised on our work.

In fact, we did not address the limitation regarding programs and generalization. We will add this discussion to Threats to Validity.

Regarding the point about slicing running time needs, we indirectly touch on that in Threats to Validity when it is mentioned that the faults from the Closure compiler project were not evaluated because of the high CPU cost of the technique. Yet, we will clarify it.

### 2019-04-18 rebuttal.md

**Rebuttal:**

We kindly thank the reviewer for the comments and questions raised on our work.

In fact, we did not address the limitation regarding programs and generalization. We will add this discussion to Threats to Validity.

The results k=10 suffer a decrease because the slicer is evaluating 10 full classes instead of only 5. For each k, we evaluate if at least one of the buggy-lines of the k classes is on the slicer report. When the 10 classes (k=10) are evaluated, there might be some of the buggy-lines that were not taken into account for k=5 that are being evaluated now and are not found in the report.

< not sure yet how to answer issue 5>

### 2019-04-18 rebuttal.md

# Paper 6364: Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization

### Review 210912:

** issue 1:**
> The approach itself, i.e., combining the mentioned debugging approaches is not that novel (as also indicated in the paper) and there are other papers describing such improvements. This is definitely a weakness of this paper. However, there is an empirical evaluation that is novel capturing important research questions.

@@

**issue 2:** Not in the paper. Should be mentioned in the paper (Threats to Validity).
> Of course – and like other similar paper – the study is limited to some programs and generalization is always questionable.

**issue 3:** 
I think the reviewer is confused because we present the results of DS two times in different tables.
> From Table 3 and Table 4 we see that basically slicing alone leads to improvements, because the values for Tandem-FL and slicing are the same.

**issue 4:** 
Explain why it can be worse.
> I am also wondering why there is a small value for commons-lang in case of k=10 when compared with k=5? I would assume that taking care of more statements should improve debugging performance.

**issue 5:** 
> In addition, there is no discussion of drawbacks behind the approach. Spectrum-based fault localization is successful because it does not require a lot of tools and can be more or less easily adapted for other programming languages. This is not the case for slicing. For slicing we require to know not only that a test case is failing but also to identify all output variables that deliver wrong values. In case of exceptions (as discussed a little bit in the paper) we may also use different slicing approaches to improve the results. There is some work on dynamic slicing in case of exceptions. Moreover, slicing needs more time for analysis and running time might become an issue.

@@

## Review 263474:

**Rebuttal:**

We kindly thank the reviewer for the comments on our work.

As we mention in section 2, applications of model-based diagnosis to localize software faults have demonstrated that can be framed as dynamic slicing by Wolfgang Mayer and Markus Stumptner in previous research which is the technique we propose to improve software fault localization. Model-based diagnosis is a well-known approach that has been proposed by the diagnosis community. This community develops algorithms and techniques that leverage AI to determine the rootcause of observed faults. We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.

### 2019-04-18 rebuttal.md

### Review 252039:

**Rebuttal:**

We kindly thank the reviewer for its insights and comments on our work.

We will make sure that the paper's formality will be improved and that the minor issues will be addressed. We will definitely explore the statistical machine learning approach in future work. Thank you for the hint!

@@

### Review 263473:

**Rebuttal:**

We kindly thank the reviewer for the feedback provided on our work.

We agree that our "theorems" are rather claims/observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed on the paper.

Regarding the question about if claim 2 is also true for other ranking algorithms, there is a possibility this might not be true. For now we decided to only focus on the ranking algorithm that provided the best results in previous research - ochiai. To answer the reviewer question precisely, the present work needs to be extended. We plan to investigate the veracity of claim 2 using other ranking algorithms, such as, Tarantula, Op2, Barinel and etc. This, however remains for future work.

Our focus in the paper was to show that dynamic slicing may considerable improve SBFL (we found an improvement of 73.7%). We decided to start with a very simple approach (critical slicing) due to its generalization, simplicity and scalability. Our idea was that if we were able to show that CS works, then later we could leverage more accurate slicing techniques to improve our results. It is also important to notice that the numbers of tools implementing this type of techniques is very small. However, we will explore this in more detail in the future.

@@

## Review 263474:

**Rebuttal:**

We kindly thank the reviewer for the comments on our work.

As we mention in section 2, applications of model-based diagnosis (MBDS) to localize software faults by Wolfgang Mayer and Markus Stumptner in previous research have demonstrated that MBDS can be framed as dynamic slicing which is the technique we propose to improve software fault localization. MBDS is a well-known approach that has been proposed by the diagnosis community. This community develops algorithms and techniques that leverage AI to determine the rootcause of observed faults. We agree that this paper will be a good suit in software engineering, validation and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.

### 2019-04-18 rebuttal.md

**issue 4:** 
Explain why it can be worse.
> I am also wondering why there is a small value for commons-lang in case of k=10 when compared with k=5? I would assume that taking care of more statements should improve debugging performance.

**Rebuttal:**

We kindly thank the reviewer for the comments and questions raised on our work.

As the title states, we intend to demystify the combination of Dynamic Slicing with Spectrum-based Fault Localization. Previous research have already shown impact and importance of both techniques - combined and separated. However, from the studies available about combining these two techniques, it was not yet clear if DS could help SBFL on obtaining more accurate results and how great would that improvement be. Thus, we find that our research questions and results might be important to guide researchers on performing research based on the combination of both techniques.

We have not address the limitation regarding programs and generalization. Thus, we will fix and add this discussion to Threats to Validity.

In table 3, we present the results for dynamic slicing alone whereas in table 4 we present the results of SFL vs. Tandem-FL for each k. Dynamic slicing in table 3 is the same as Tandem-FL in table 4. Thus, the values are the same. We only presented the same results in different views. On table 3, we intend to show the evolution of Tandem-FL/dynamic slicing between different k's (k=5 and k=10) and focus solely on the dynamic slicing performance on finding faulty statements for different k's. Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k. We understand that this might create some confusion. Thus, we will try to improve it.

_The results k=10 suffer a decrease because the slicer is evaluating 10 full classes instead of only 5. For each k, we evaluate if at least one of the buggy-lines of the k classes is on the slicer report. When the 10 classes (k=10) of fault are evaluated, there might be some of the buggy-lines that were not taken into account for k=5 that are being evaluated now and are not found in the report._ (!! not finished yet)

These techniques have a few pratical limitations. We can only ensure that the proposed technique will work with defects4j programs because we generalized our function of interess according with the type of failling tests messages that exist on the dataset. Thus, some messages with very specific characteristics may not provide valide results. However, we intend to make clear what type of observed faults the tools is able to evaluate and turn the tool open-source after publishing it. Analysis and running time it is an issue, specially, in programs where the codebases are larger such as the Closure Compiler. Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.

### 2019-04-18 rebuttal.md

### Review 210912:

**Rebuttal:**

We kindly thank the reviewer for the comments and questions raised on our work.

As the title states, we intend to demystify the combination of Dynamic Slicing with Spectrum-based Fault Localization. Previous research has already shown the impact and importance of both techniques - combined and separated. However, from the studies available about combining these two techniques, it was not yet clear if DS could help SBFL on obtaining more accurate results and how great would that improvement be. Thus, we find that our research questions and results might be important to guide researchers on performing research based on the combination of both techniques.

We have not addressed the limitation regarding programs and generalization. Thus, we will fix and add this discussion to Threats to Validity.

@@

In table 3, we present the results for dynamic slicing alone whereas in table 4 we present the results of SFL vs. Tandem-FL for each k. Dynamic slicing in table 3 is the same as Tandem-FL in table 4. Thus, the values are the same. We only presented the same results in different views. On table 3, we intend to show the evolution of Tandem-FL/dynamic slicing between different k's (k=5 and k=10) and focus solely on the dynamic slicing performance on finding faulty statements for different k's. Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k. We understand that this might create some confusion. Thus, we will try to improve it.

In commons-lang, the performance of capturing faulty statements of k=10 should be equal to k=5 or higher. The 100% cases for k=5 include two faults of omission (limitation mentioned in RQ3) which were not filtered when the report was retrieved. We apologize for that, the mistake has been fixed.

These techniques have a few practical limitations. We can only ensure that the proposed technique will work with defects4j programs because we generalized our function of interest according to the type of failing tests messages that exist on the dataset. Thus, some messages with very specific characteristics may not provide valid results. However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing it. Analysis and running time it is an issue, especially, in programs where the codebases are larger such as the Closure Compiler. Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.
### Review 252039:

@@

### Review 263473:

**Rebuttal:**

We kindly thank the reviewer for the feedback provided on our work.

We agree that our "theorems" are rather claims/observations or properties of the ranking algorithm. Thus, these misconceptions will be addressed in the paper.

Regarding the question about if claim 2 is also true for other ranking algorithms, there is a possibility this might not be true. For now, we decided to only focus on the ranking algorithm that provided the best results in previous research - Ochiai. To answer the reviewer question precisely, the present work needs to be extended. We plan to investigate the veracity of claim 2 using other ranking algorithms, such as Tarantula, Op2, Barinel and etc. This, however, remains for future work.

Our focus in the paper was to show that dynamic slicing may considerably improve SBFL (we found an improvement of 73.7%). We decided to start with a very simple approach (critical slicing) due to its generalization, simplicity, and scalability. Our idea was that if we were able to show that CS works, then later we could leverage more accurate slicing techniques to improve our results. It is also important to notice that the numbers of tools implementing this type of technique is very small. However, we will explore this in more detail in the future.

@@

## Review 263474:

**Rebuttal:**

We kindly thank the reviewer for the comments on our work.

As we mentioned in section 2, applications of model-based diagnosis (MBDS) to localize software faults by Wolfgang Mayer and Markus Stumptner has demonstrated that MBDS can be framed as dynamic slicing which is the technique we propose to improve software fault localization. MBDS is a well-known approach that has been proposed by the diagnosis community. This community develops algorithms and techniques that leverage AI to determine the root cause of observed faults. We agree that this paper will be a good suit in software engineering, validation, and testing conferences but we also strongly believe that this paper can be published at IJCAI since we are applying AI to improve SBFL.

### 2019-04-18 rebuttal.md

### Review 252039:

**Rebuttal:**

We kindly thank the reviewer for its insights and comments on our work.

We will ascertain that the paper's formality will be improved as well as the minor issues will be addressed. Exploring the statistical machine learning approach remains as future work.

@@

### Review 263473:

**Rebuttal:**

We kindly thank the reviewer for the feedback provided on our work.

We agree that the "theorems" are rather claims/observations or properties of the ranking algorithm. Following the suggestion of one of reviewers, we will rename them as "claims".

Regarding the question whether claim 2 is also valid for other ranking algorithms, there is a possibility this might not be true. For now, we decided to only focus on the ranking algorithm that provided the best results in previous research - Ochiai. To answer the reviewer question accurately, the present work needs to be extended. We plan to investigate the veracity of claim 2 using other ranking algorithms, such as Tarantula, Op2, Barinel. This, however, remains for future work.

The focus of the paper is to show that dynamic slicing considerably improves SBFL (we found an improvement of 73.7%). We decided to start with a very simple approach (critical slicing) due to its generalization, simplicity, and scalability. We argue that if we are able to show that CS works, then the results could be further improved by using more accurate slicing techniques. It is also important to notice that the numbers of tools implementing slicing is rather limited.

@@

## Review 263474:

**Rebuttal:**

We kindly thank the reviewer for the comments on our work.

As we mentioned in section 2, applications of model-based diagnosis (MBDS) to localize software faults by Wolfgang Mayer and Markus Stumptner has demonstrated that MBDS can be framed as dynamic slicing which is the technique we propose to improve software fault localization. MBDS is a well-known approach that has been proposed by the diagnosis community, an AI sub-community. We agree that this paper will also be a good suit in software engineering, validation, and testing conferences but we also strongly argue that this paper is of interest of the IJCAI audience, since we are applying an AI-based technique to improve SBFL.

### 2019-04-18 rebuttal.md

### Review 210912:

**Rebuttal:**

We kindly thank the reviewer for the comments and questions raised on our work.

This paper is not intended to propose a new approach, but, instead, to demystify the combination of dynamic slicing and SFL. There are previous works which show the value of combining both techniques. However, the applicability of the techniques proposed by related work are questionable because they used rather small programs and seeded faults. The contribution of our paper is to demonstrate that combining both techniques work for real and large programs.

We agree with the reviewer that our empirical study is limited to some programs and therefore the generalization is always questionable. We will improve our discussion in the Threats to Validity section regarding this issue.

In Table 3, we present the results for dynamic slicing alone whereas in Table 4 we present the results of SFL vs. Tandem-FL for each k. Dynamic slicing in table 3 is the same as Tandem-FL in table 4. Thus, the values are the same. We only presented the same results in different views. On table 3, we intend to show the evolution of Tandem-FL/dynamic slicing between different k's (k=5 and k=10) and focus solely on the dynamic slicing performance on finding faulty statements for different k's. Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k. We understand that this might create some confusion, and will be clarified.

@@

## Review 263474:

**Rebuttal:**

We kindly thank the reviewer for the comments on our work.

As we mentioned in section 2, a previous studies have demonstrated that Model-based software diagnosis can be framed as dynamic slicing. This is a well-known approach that has been proposed by the diagnosis community, an AI sub-community. We agree that this paper will also be a good suit in software engineering, validation, and testing conferences but we also strongly argue that this paper is of interest of the IJCAI audience, since we are applying an AI-based technique to improve SBFL.

### 2019-04-18 rebuttal.md

We agree with the reviewer that our empirical study is limited to some programs and therefore the generalization is always questionable. We will improve our discussion in the Threats to Validity section regarding this issue.

In Table 3, we present the results for dynamic slicing alone whereas in Table 4 we present the results of SFL vs. Tandem-FL for each k. Dynamic slicing in table 3 is the same as Tandem-FL in table 4. Thus, the values are the same. We only presented the same results in different views. On table 3, we intend to show the evolution of Tandem-FL/dynamic slicing between different k's (k=5 and k=10) and focus solely on the dynamic slicing performance on finding faulty statements for different k's. Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k. We understand that this might create some confusion, and will be clarified.

In commons-lang, the performance of capturing faulty statements of k=10 should be equal to k=5 or higher. The 100% cases for k=5 include two faults of omission (limitation mentioned in RQ3) which were not filtered when the report was retrieved. We apologize for that, the mistake has been fixed.

These techniques have a few practical limitations. We can only ensure that the proposed technique will work with Defects4j programs because we generalized our function of interest according to the type of failing tests messages that exist on the dataset. Thus, some messages with very specific characteristics may not provide valid results. However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing it. Analysis and running time it is an issue, especially, in programs where the codebases are larger such as the Closure Compiler. Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.

### 2019-04-18 rebuttal.md

We kindly thank the reviewer for the comments and questions raised on our work.

This paper is not intended to propose a new approach, but, instead, to demystify the combination of dynamic slicing and SFL. There are previous works which show the value of combining both techniques. However, the applicability of the techniques proposed by related work are questionable because they used rather small programs and seeded faults. The contribution of our paper is to demonstrate that combining both techniques work for real and large programs.

We agree with the reviewer that our empirical study is limited to some programs and therefore the generalization is always questionable. We will improve our discussion in the Threats to Validity section regarding this issue.

[very problematic/confusing]
In Table 3, we present the results for dynamic slicing alone whereas in Table 4 we present the results of SFL vs. Tandem-FL for each k. Dynamic slicing in table 3 is the same as Tandem-FL in table 4. Thus, the values are the same. We only presented the same results in different views. On table 3, we intend to show the evolution of Tandem-FL/dynamic slicing between different k's (k=5 and k=10) and focus solely on the dynamic slicing performance on finding faulty statements for different k's. Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k. We understand that this might create some confusion, and will be clarified.

[Problematic Text: this leads to a reject! No apologies.]
In commons-lang, the performance of capturing faulty statements of k=10 should be equal to k=5 or higher. The 100% cases for k=5 include two faults of omission (limitation mentioned in RQ3) which were not filtered when the report was retrieved. We apologize for that, the mistake has been fixed.

### 2019-04-19 rebuttal.md

We kindly thank the reviewer for the comments and questions raised on our work.

This paper is not intended to propose a new approach, but, instead, to demystify the combination of dynamic slicing and SFL. There are previous works which show the value of combining both techniques. However, the applicability of the techniques proposed by related work are questionable because they used rather small programs and seeded faults. The contribution of our paper is to demonstrate that combining both techniques work for real and large programs.

We agree with the reviewer that our empirical study is limited to some programs and therefore the generalization is always questionable. We will improve our discussion in the Threats to Validity section regarding this issue.

Table 3 and 4 are the different present different views to answer RQ2.

@@

In Table 3, we present the results for dynamic slicing alone whereas in Table 4 we present the results of SFL vs. Tandem-FL for each k. Dynamic slicing in table 3 is the same as Tandem-FL in table 4. Thus, the values are the same. We only presented the same results in different views. On table 3, we intend to show the evolution of Tandem-FL/dynamic slicing between different k's (k=5 and k=10) and focus solely on the dynamic slicing performance on finding faulty statements for different k's. Whereas, in table 4, our goal is to show the difference between SFL and Tandem-FL for each k. We understand that this might create some confusion, and will be clarified.

We double-checked the empirical results and the decrease observed in table 3 and 4 for commons-lang is a typo. The percentage of faults for k=5 is also 96.9%. We have double-checked all other values, they stand correct. This will be fixed.

### 2019-04-19 rebuttal.md

We kindly thank the reviewer for the comments and questions raised on our work.

This paper is not intended to propose a new approach, but, instead, to demystify the combination of dynamic slicing and SFL. There are previous works which show the value of combining both techniques. However, the applicability of the techniques proposed by related work are questionable because they used rather small programs and seeded faults. The contribution of our paper is to demonstrate that combining both techniques work for real and large programs.

We agree with the reviewer that our empirical study is limited to some programs and therefore the generalization is always questionable. We will improve our discussion in the Threats to Validity section regarding this issue.

Table 3 and 4 are present different views to answer RQ2. [missing 2nd part of DS vs Tandem-FL and DS being a set]

### 2019-04-19 rebuttal.md

**Rebuttal:**

We kindly thank the reviewer for the comments and questions raised on our work.

This paper is not intended to propose a new approach, but, instead, to demystify the combination of dynamic slicing and SFL. There are previous works which show the value of combining both techniques. However, the applicability of the techniques proposed by related work are questionable because they used rather small programs and seeded faults. The contribution of our paper is to demonstrate that combining both techniques work for real and large programs.

We agree with the reviewer that the conclusions we can draw from our empirical study is limited to the used programs and therefore the generalization is always questionable. We will improve our discussion in the Threats to Validity section regarding this issue.

Table 3 and 4 present different views to answer RQ2, and should be clarified. As dynamic slicing produces a set, hence not being possible to select the top-k components, what is reported in Table 3 is Tandem-FL. Our decision to call it dynamic slicing alone was unfortunate and leads to confusion. Perhaps the best is to only include current table 4.

After double-checking the empirical results, the decrease in table 3 and 4 for commons-lang is due to a typo. The percentage of faults for k=5 is also 96.9%. Further, we double-checked all other values, they stand correct. This will be fixed.

It is a fact that the implementation of our approach does not come without practical limitations. We can only ensure that the current implementation works with Defects4j programs only because we generalized our function of interest according to the type of failing messages that exist on the dataset. Thus, some messages with specific characteristics may not provide valid results in other datasets. However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing the paper. Analysis and running time may be an issue, especially, in programs where the codebases are rather large. Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.

### 2019-04-19 rebuttal.md

**Rebuttal:**

We kindly thank the reviewer for the comments and questions raised on our work.

This paper is not intended to propose a new approach, but, instead, to demystify the combination of dynamic slicing and SFL. There are previous works which show the value of combining both techniques. However, the applicability of the techniques proposed by related work are questionable because they used rather small programs and seeded faults. The contribution of our paper is to demonstrate that combining both techniques work for real and large programs.

We agree with the reviewer that the conclusions we can draw from our empirical study are limited to the used programs and therefore the generalization is always questionable. We will improve our discussion in the Threats to Validity section regarding this issue.

Table 3 and 4 show different views we thought were adequate to answer RQ2, but we realize that they should be further clarified. As dynamic slicing produces a set, hence not being possible to select the top-k components, what is reported in Table 3 is Tandem-FL. Our decision to call it dynamic slicing alone was unfortunate and leads to confusion. Perhaps the best is to only include current table 4.

After double-checking the empirical results, the decrease in table 3 and 4 for commons-lang is due to a typo. The percentage of faults for k=5 is also 96.9%. Further, we double-checked all other values, they stand correct. This will be clarified.

### 2019-04-19 rebuttal.md

### Review 252039:

**Rebuttal:**

We kindly thank the reviewer for its insights and comments on our work.

We will ascertain that the paper's formality will be improved as well as the minor issues will be addressed. Exploring the statistical machine learning approach remains as future work, though.

@@

## Review 263474:

**Rebuttal:**

We kindly thank the reviewer for the comments on our work.

As we mentioned in section 2, previous studies have demonstrated that Model-based software diagnosis (MBSD) can be framed as dynamic slicing. MBSD is a well-known approach that has been proposed by the diagnosis community, an AI sub-community. We agree that this paper will also be a good suit in software engineering, validation, and testing conferences but we also strongly argue that this paper is of interest of the IJCAI audience.

### 2019-04-19 rebuttal.md

# Paper 6364: Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization

### Review 210912:

**Rebuttal:**

Thank you for the constructive review.

This paper is not intended to propose a new approach, but, instead, to reassess the impact of an existing approach that combines dynamic slicing and Spectrum-based Fault Localization. Previous works show the effect of combining both techniques. However, results were inconclusive---they used rather small programs (because of limitations on their infrastructure), small number of faults, and evaluation metrics that can inflate diagnosis performance. The central contribution of our paper is to demonstrate that combining both techniques work for real and large programs.

We agree with the reviewer that the conclusions we can draw from our empirical study are limited to the used programs and therefore generalization is always questionable. We will improve our discussion in the Threats to Validity section regarding this issue.

Tables 3 and 4 show different views we thought were adequate to answer RQ2, but we realize that they should be further clarified. Dynamic slicing produces a set of components (e.g., statements). As such, it is not possible to rank results and select the top-k components. For that reason, Table 3 reports the results of Tandem-FL. Our decision to call it dynamic slicing alone was unfortunate and leads to confusion. Perhaps the best is to only include current table 4.

After double-checking the empirical results, we found that the decrease in value pointes on tables 3 and 4 for commons-lang is due to a typo. The percentage of faults for k=5 is also 96.9%. We double-checked all other values, and confirm that are correct. This will be clarified.

It is a fact that the implementation of our approach does not come without practical limitations. We can only ensure that the current implementation works with Defects4j programs only because we generalized our function of interest according to the type of failing messages that exist on the dataset. This generalization does not cover all cases. Although this can be customized, as it is, lithium-slicer may not produce valid results in other datasets. However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing the paper. Analysis and running time may be an issue, especially for programs where the codebases are rather large. Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.

### 2019-04-19 rebuttal.md

# Paper 6364: Demystifying the Combination of Dynamic Slicing and Spectrum-based Fault Localization

### Review 210912:

**Rebuttal:**

Thanks for the constructive review.

This paper is not intended to propose a new approach, but to reassess the impact of combining dynamic slicing and Spectrum-based Fault Localization. Previous works reported inconclusive results---they used rather small programs/faults (limitations on their infrastructure) and evaluation metrics that can inflate diagnosis performance. Our central contribution is to demonstrate that combining both techniques works for real/large programs.

We agree that the conclusions drawn from our empirical study are limited to the programs used, hence questionable generalization. We will improve our discussion in the Threats to Validity section regarding this issue.

Tables 3-4 show views we thought were adequate to answer RQ2, but we realize that they should be clarified. Dynamic slicing produces a set of components (e.g., statements). As such, it is not possible to rank results and select the top-k components. For that reason, Table 3 reports the results of Tandem-FL. Our decision to call it dynamic slicing alone was unfortunate and leads to confusion. Perhaps the best is to only include table 4.

@@

After double-checking the empirical results, we found that the decrease in value pointes on tables 3 and 4 for commons-lang is due to a typo. The percentage of faults for k=5 is also 96.9%. We double-checked all other values, and confirm that are correct. This will be clarified.

It is a fact that the implementation of our approach does not come without limitations. We only ensure that the current implementation works with Defects4j programs because we generalized the function of interest given the failing observed. This generalization does not cover all cases. Although this can be customized, as it is, lithium-slicer may not produce valid results in other datasets. However, we intend to make clear what type of observed faults the tool is able to evaluate and turn the tool open-source after publishing the paper. Analysis and running time may be an issue, especially for programs where the codebases are rather large. Therefore, we also plan to take action on this point and add parallelization mechanisms to this type of techniques.

@@

We kindly thank the reviewer for the feedback provided on our work.

We agree that the "theorems" are rather claims/observations or properties of the ranking algorithm. Following the suggestion of one of reviewers, we will rename them as "claims".

Regarding the question whether claim 2 is also valid for other ranking algorithms, there is a possibility this might not be true. For now, we decided to only focus on the ranking algorithm that provided the best results in previous research - Ochiai. To answer the reviewer question accurately, the present work needs to be extended. We plan to investigate the veracity of claim 2 using other ranking algorithms, such as Tarantula, Op2, Barinel. This, however, remains for future work.

The focus of the paper is to show that dynamic slicing considerably improves SBFL (we found an improvement of 73.7%). We decided to start with a very simple approach (critical slicing) for its generality, simplicity, and scalability. We argue that if we are able to show that CS works, then the results could be further improved by using more accurate slicing techniques. It is also important to notice that the numbers of tools implementing slicing is rather limited.

### 2019-05-12 paper/ijcai/rebuttal.md

### Review 210912:

**Rebuttal:**

Thanks for the constructive review.

This paper is not intended to propose a new approach, but to reassess the impact of combining dynamic slicing and Spectrum-based Fault Localization. Previous works reported inconclusive results---they used rather small programs (infrastructure limitations) and evaluation metrics that can inflate diagnosis performance. Our central contribution is to demonstrate that combining both techniques works for real/large programs.
We agree that the conclusions drawn from our empirical study are limited to the programs used, hence questionable generalization. We will improve our discussion in the Threats to Validity section.

Tables 3-4 show views we thought were adequate to answer RQ2, but we realize that they should be clarified. Dynamic slicing produces a set of components. As such, it is not possible to rank results and select the top-k components. For that reason, Table 3 reports the results of Tandem-FL. Our decision to call it dynamic slicing alone was unfortunate and leads to confusion. Perhaps the best is to only include table 4.

After double-checking the empirical results, we found that the decrease in tables 3-4 for commons-lang is due to a typo. The percentage of faults for k=5 is also 96.9%. All other values were confirmed and are correct. This will be clarified.

The implementation of our approach does not come without limitations. We only ensure that the current implementation works with Defects4j programs because we generalized the function of interest given the failing observed, which does not cover all cases. Although this can be customized, as it is, lithium-slicer may not produce valid results in other datasets. We intend to clarify what type of observed faults the tool is able to evaluate and turn it open-source after publication. Analysis and running time may be an issue, especially for programs where the codebases are rather large which can be softened through the application of parallel programming to dynamic slicing.
